Ground state energy of quantum dots using the coupled cluster method

### 2018-05-11 project_2/article/article.tex
Add link to crawdad
Begin doubles amplitudes

    \subsection{Coupled cluster amplitude equations}
        In order for us to solve the energy equation using the coupled cluster
        approximation we need to figure out what the cluster amplitudes,
        $t_{ij\dots}^{ab\dots}$, are. This is done by projecting
        \autoref{eq:clean_schrodinger} onto an excited Slater determinant, i.e.,
        \begin{align}
            \bra{\Phi_{ij\dots}^{ab\dots}}e^{-T}He^{T}\kslat
            = 0.
        \end{align}
        Note that in the amplitude equations we can use both the regular and the
        normal ordered Hamiltonian. They are equal as the reference energy term
        disappears due to \autoref{eq:excited_overlap}. The order of the
        excitation in the projection determines the order of the amplitudes you
        will find. In our case we are only interested in the second order
        ampltiudes found in the doubles approximation, hence we will solve the
        equation
        \begin{align}
            \bra{\Phi_{ij}^{ab}}e^{-T}H_N e^{T}\kslat = 0,
        \end{align}
        to find an expression that can be used to solve for $t_{ij}^{ab}$.

@@

>>>>

    \subsection{Coupled cluster amplitude equations}
        In order for us to solve the energy equation using the coupled cluster
        approximation we need to figure out what the cluster amplitudes,
        $t_{ij\dots}^{ab\dots}$, are. This is done by projecting
        \autoref{eq:clean_schrodinger} onto an excited Slater determinant, i.e.,
        \begin{align}
            \bra{\Phi_{ij\dots}^{ab\dots}}e^{-T}He^{T}\kslat
            = 0.
        \end{align}
        Note that in the amplitude equations we can use both the regular and the
        normal ordered Hamiltonian. They are equal as the reference energy term
        disappears due to \autoref{eq:excited_overlap}. The order of the
        excitation in the projection determines the order of the amplitudes you
        will find. In our case we are only interested in the second order
        ampltiudes found in the doubles approximation, hence we will solve the
        equation
        \begin{align}
            \bra{\Phi_{ij}^{ab}}e^{-T}H_N e^{T}\kslat = 0,
            \label{eq:doubles_amplitude_1}
        \end{align}
        to find an expression that can be used to solve for $t_{ij}^{ab}$.
        By employing the Baker-Campbell-Haussdorf (BCH) expansion we find
        \begin{equation}
        \begin{aligned}
        		\bar{H} 
        			=& \Big(
        					H_N + H_NT_1 + H_NT_2 + \frac{1}{2}H_NT_1^2 
        					+ \frac{1}{2}H_NT_2^2 \\
        				  &+ H_NT_1T_2 + \frac{1}{6}H_NT_1^3 
        				    + \frac{1}{2}H_NT_1^2T_2 + \frac{1}{2}H_NT_1T_2^2 \\
        				  &+ \frac{1}{6}H_NT_2^3 + \frac{1}{24}H_NT_1^4 
        				    + \frac{1}{6}H_NT_1^3T_2 \\
        				 &+ \frac{1}{6}H_NT_1^2T_2^2 + \frac{1}{6}H_NT_1T_2^3
        				   + \frac{1}{24} H_NT_2^4
        				 \Big)_c.
        \end{aligned}
        \label{eq:normal_order_expansion}
        \end{equation}
		The subscript $c$ indicates that only those terms in which the 
		Hamiltonian is connected\footnote{In a Wick's theorem sense}
		to every cluster operator on its right should be included. Since
		the Hamiltonian contains at most four annihilation and creation 
		operators, $H_N$ can connect to at most four cluster operators
		at once. Therefor, the BCH expansion must truncate at the
		fourth-order terms.

		Now comes the rather tedious task of evaluating all the terms 
		that arises from inserting \autoref{eq:normal_order_expansion}
		into \autoref{eq:doubles_amplitude_1}. The first of such terms
		is
		\begin{equation}
		\begin{aligned}
			\bra{\Phi_{ij}^{ab}} &(F_N + V_N)\ket{\Phi_0} \\
			 =& \sum_{pq}f_{pq}\bra{\Phi_0}\{a_i^\dagger a_j^\dagger a_ba_a\}\{a^\dagger_pa_q\}\ket{\Phi_0} \\
			 &+\frac{1}{4}\sum_{pqrs}\bra{pq}\ket{rs}
			 \bra{\Phi_0}\{a_i^\dagger a_j^\dagger a_ba_a\}\{a^\dagger_pa^\dagger_qa_sa_r\}\ket{\Phi_0}
		\end{aligned}
		\end{equation}

@@

            % See Step 3 in:
            % http://sirius.chem.vt.edu/wiki/doku.php?id=crawdad:programming:project4
